---
title: "Multilevel Model"
output:
  html_document:
    toc: true
    toc_float: true
    theme: spacelab
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE,
                      echo = TRUE,
                      fig.width = 10,
                      fig.height = 10,
                      dev.args = list(bg="transparent"))

library(tidyverse)
require(nlme)
library(here)
library(rio)

data <- import(here("data", "mlm_data.csv"),
               setclass = "tbl_df") 

head(data)
```


### Null (unconditional) model

```{r}
d.Null <- lme(DV~1,random=~1|Case,data=data,
control=list(opt="optim"),na.action="na.omit")
coefficients(d.Null)
intervals(d.Null)
summary(d.Null)
```


### Model with random intercept and change in level (with an autocorrelation component)
```{r}
d.Level <- lme(DV~1+Phase,random=~1|Case,data=data,
correlation=corAR1(form=~1|Case),control=list(opt="optim"),na.action="na.omit")
coefficients(d.Level)
intervals(d.Level)
summary(d.Level)
```


### Model with random intercept and change in slope (with an autocorrelation component)
```{r}
d.Time <- lme(DV~1+Time_CTR,random=~1|Case,data=data,
correlation=corAR1(form=~1|Case),control=list(opt="optim"),na.action="na.omit")
# Rename variables and use only complete cases
coefficients(d.Time)
intervals(d.Time)
summary(d.Time)
```


### Model with random intercept and change in level/slope in Tx (with autocorrelation)
```{r}
d.Model <- lme(DV~1+Phase+Time_PhaseCTR,random=~1|Case,data=data,
correlation=corAR1(form=~1|Case),control=list(opt="optim"),na.action="na.omit")

# Rename variables and use only complete cases
coefficients(d.Model)
intervals(d.Model)
summary(d.Model)
```

### Results


| **Value** | **Score** | **_p_-Value** |
| :-------- | :-------: | :-----------: |
| Autocorrelation     | .494      |  |
| Effect size of change between phases | 10.17      | .177 |
| Slope | 1.84     |  .337    |


Although the effect size is rather large, it is not significant. Additionally, the obtained change in slope between phases is not significant. This does not necessarily suggest a functional relation cannot be determined. As defined in Carter (2013): _effect size_ does not imply causation and effect sizes are independent of demonstrations of experimental control. I think this is worth taking into consideration when comparing this calculation to the visual analysis and Tau-U. 


