---
title: "Visual Analysis"
output:
  html_document:
    toc: true
    toc_float: true
    theme: spacelab
    highlight: tango
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r setup 1, include=FALSE}
library(tidyverse)
library(rio)
library(here)
library(gghighlight)
library(forcats)
library(ggrepel)
library(gt)
library(knitr)
library(kableExtra)
library(reactable)
library(plotly)
library(SCVA)
library(patchwork)
library(colorblindr)
library(scan)
theme_set(theme_minimal(15) +
            theme(legend.position = "bottom",
                  panel.grid.major.x = element_line(color = "gray60"),
                  panel.grid.minor.x = element_blank(),
                  panel.grid.major.y = element_blank())
          )

kahi <- import(here("data", "KAHI_status_goal.xlsx"),
               setclass = "tbl_df") 

gasy <- import(here("data", "GASY_status_goal.xlsx"),
               setclass = "tbl_df") 

gozo <- import(here("data", "GOZO_status_goal.xlsx"),
               setclass = "tbl_df") 
 
```


## Patchwork Code 

Most likely, this is the plot that will be used in the final manuscript. The plots were created individually in Rstudio with the ggplot package. They are then stacked together with the patchwork package to create one image. I intend to save this image and upload it into PowerPoint to add the dashed line between baselines and text identifiers (e.g., phases, participants)

```{r, include=FALSE}
head(kahi)

kahi_plot <- ggplot() +
  geom_line(data = kahi, aes(x = session, y = bl)) +
  geom_point(data = kahi, aes(x = session, y = bl), size = 2) +
  geom_line(data = kahi, aes(x = session, y = tx)) +
  geom_point(data = kahi, aes(x = session, y = tx), size = 2) +
  scale_x_continuous(limits = c(0, 13),
                     breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13)) +
  scale_y_continuous(limits = c(0, 60),
                     breaks = c(0, 5, 10, 15, 20, 25, 30, 35, 40, 45, 50, 55, 60)) +
  theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.line.x = element_blank()) +
  labs(x = "Session",
       y = "Minutes Engaged\n in Online Literature Lecture\n (Average between Two Classes)") 

kahi_plot


gasy_plot <- ggplot() +
  geom_line(data = gasy, aes(x = session, y = bl)) +
  geom_point(data = gasy, aes(x = session, y = bl), size = 2) +
  geom_line(data = gasy, aes(x = session, y = tx)) +
  geom_point(data = gasy, aes(x = session, y = tx), size = 2) +
  scale_x_continuous(limits = c(0, 13),
                     breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13)) +
  scale_y_continuous(limits = c(0, 60),
                     breaks = c(0, 5, 10, 15, 20, 25, 30, 35, 40, 45, 50, 55, 60)) +
  theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.line.x = element_blank()) +
  labs(x = "Session",
       y = "Minutes per Week Spent\n Studying for Spanish Class") 


gasy_plot


gozo_plot <- ggplot() +
  geom_line(data = gozo, aes(x = session, y = bl)) +
  geom_point(data = gozo, aes(x = session, y = bl), size = 2) +
  geom_line(data = gozo, aes(x = session, y = tx)) +
  geom_point(data = gozo, aes(x = session, y = tx), size = 2) +
  scale_x_continuous(limits = c(0, 13),
                     breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13)) +
  scale_y_continuous(limits = c(0, 100),
                     breaks = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100)) +
  theme_classic() +
  labs(x = "Session",
       y = "Percentage of Weekly\n Assignments Completed") 


gozo_plot


all_plots <- gasy_plot / kahi_plot / gozo_plot

all_plots
```

```{r, include=TRUE, fig.height=9, fig.width=10}
all_plots
```


## SCAN Demonstration {.tabset .tabset-fade .tabset-pills}

These are plots created with the SCAN package, which is a R packaged designed specifically the plot and analyze single case research data. 

```{r, include=FALSE}
case_1 <- scdf(
  values = c(A = 10, 5, 15, B = 5, 25, 20, 60, 30, 10, 5, 10, 60, 30), 
  name = "GASY"
)

case_2 <- scdf(
  values = c(A = 10, 10, 10, 3, 10, 10, B = 15, 35, 15, 30, 20, 23, 30), 
  name = "KAHI"
)

case_3 <- scdf(
  values = c(A = 25, 26.32, 35.71, 45.83, 62.5, 88.89, 62.5, 69.57, 
             B = 70, 69.57, 60, 60.71, 66), 
  name = "GOZO"
)

all_mbl_data <- c(case_1, case_2, case_3)
```


```{r, include=FALSE}
marks <- list(
  positions = list( c(8, 9), c(17, 19), c(7, 18) ), 
  col = 'red', cex = 2.5, pch = 1
)

plot(exampleAB, marks = marks, style = "sienna")

head(exampleAB)
exampleAB

plot(exampleAB)
plot(all_mbl_data) 
```

### Version 1

```{r, include=TRUE, fig.height=8, fig.width=10}
plot(all_mbl_data)
```

```{r, include=FALSE}
plot_style = style_plotSC(style = "chart",
                          fill = "grey50",
                          grid = "lightblue",
                          pch = 16)
plot_v2 <- plot(
  all_mbl_data,
  xlab = "session",
  ylab = "Participant Measurement",
  phase.names = c("Baseline", "Treatment"),
  ylim = c(0, 100),
  style = plot_style)
```

### Version 2

```{r, include=TRUE, fig.height=8, fig.width=10}
plot(
  all_mbl_data,
  xlab = "session",
  ylab = "Participant Measurement",
  phase.names = c("Baseline", "Treatment"),
  ylim = c(0, 100),
  style = plot_style)
```